### 2018-06-19 doc/latex/02-Software.tex
Fix <
Fixes

Stride is written in C++ and portable over all platforms that have the GNU C++ compiler. 
To use the visualization tools Qt is needed (at least version 5.9), besides that the following tools needs to be installed:
\begin{compactitem}
    \item g++
    \item make
    \item CMake (>= v3.10)
    \item Boost
    \item Python (optional, for automatization)
    \item Doxygen (optional, for documentation)
    \item LaTeX (optional, for documentation)
\end{compactitem}

@@

To install the project, first obtain the source code by cloning the repository to a directory or download a zip file with all project
material from the GitHub website and de-compress the archive. 
The build system for Stride uses the CMake tool. This is used to build and install the software at a high level of abstraction and almost platform independent (see \url{http://www.cmake.org/}). 
The project includes the conventional make targets to ``build'', ``install'', ``test'' and ``clean'' the project. There is one additional target ``configure'' to set up the CMake/make structure that will actually do all the work.
For those users that do not have a working knowledge of CMake, a front end Makefile has been provided that invokes the appropriate CMake commands.
More details on building the software can be found in ``INSTALL.txt'' in the source folder.

>>>>

Stride is written in C++ and portable over all platforms that have the GNU C++ compiler. 
The following tools needs to be installed:
\begin{compactitem}
    \item g++
    \item make
    \item CMake (\textgreater = v3.10)
    \item Boost
    \item Qt (\textgreater = 5.9, optional, for visualization)
    \item Python (optional, for automatization)
    \item Doxygen (optional, for documentation)
    \item LaTeX (optional, for documentation)
\end{compactitem}

@@

To install the project, first obtain the source code by cloning the repository to a directory .
The build system for Stride uses the CMake tool. This is used to build and install the software at a high level of abstraction and almost platform independent (see \url{http://www.cmake.org/}). 
The project includes the conventional make targets to ``build'', ``install'', ``test'' and ``clean'' the project. There is one additional target ``configure'' to set up the CMake/make structure that will actually do all the work.
For those users that do not have a working knowledge of CMake, a front end Makefile has been provided that invokes the appropriate CMake commands.
More details on building the software can be found in ``INSTALL.txt'' in the source folder.

### 2018-06-19 doc/latex/03-Simulator.tex
Fixes

        \item $DE\_cities.csv$: German cities, fetched from \footnote{\url{}}.
        \item $FR\_cities.csv$: French cities, fetched from \footnote{\url{}}.
        \item $NL\_cities.csv$: Dutch cities, fetched from \footnote{\url{}}.
        \item $wallonia\_cities.csv$: Wallonia cities, fetched from \footnote{\url{}}.
        \item $submunicipalities.csv$: Belgian sub-municipalities, fetched from \footnote{\url{}}.
        \end{itemize}
    \item Documentation files
      	in directory \texttt{./target/installed/doc}
      	\begin{itemize}
        		\item Reference manual
        		\item User manual
        \end{itemize}
\end{compactitem}

@@

\begin{description}
    \item[\texttt{--config}] \ \\
        Specifies the run configuration parameters to be used for the simulation.
        If this is provided multiple times, the calibration is performed on all given simulations.
        It may be either -c file= \textless file \textgreater or -c name= \textless name \textgreater .
        The first option can be shortened to -c \textless file \textgreater , the second option accepts \texttt{TestsInfluenza}, \texttt{TestsMeasles} or \texttt{BenchMeasles} as  \textless name \textgreater .
    \item[\texttt{--testcases}] \ \\
        Instead of providing the configuration files, you can also select multiple testcases to use for the simulation runs.
        The default is \texttt{influenza\_a, influenza\_b, influenza\_c, measles\_16} and \texttt{r0\_12}.
    \item[\texttt{--multiple}]\ \\
        The amount of simulations to run for each testcase. For each simulation, a different seed will be used.
    \item[\texttt{--single}]\ \\
        Run the simulations with the fixed seeds to determine the exact values.
    \item[\texttt{--output}]\ \\
        Write the results of the calibration to a file with given filename.
        This resulting file contains for each configuration and each step in the simulation the mean, standard deviation, exact value using the default seed and the values found with other seeds.
        These values depend on the selected options, specifically \texttt{--multiple} and \texttt{--single}.
    \item[\texttt{--write}]\ \\
        Write boxplots to files in the current directory. This creates an image for each config or testcase.
    \item[\texttt{--display}]\ \\
        Display the boxplots for the last step.
    \item[\texttt{--displayStep}]\ \\
        Display the boxplots for a specified step.
\end{description}

>>>>

        \item $DE\_cities.csv$: German cities, fetched from \footnote{\url{https://en.wikipedia.org/wiki/List\_of\_cities\_and\_towns\_in\_Germany}}.
        \item $FR\_cities.csv$: French cities, fetched from \footnote{\url{https://en.wikipedia.org/wiki/List\_of\_arrondissements\_of\_France}}.
        \item $NL\_cities.csv$: Dutch cities, fetched from \footnote{\url{https://nl.wikipedia.org/wiki/Tabel\_van\_Nederlandse\_gemeenten}}.
        \item $wallonia\_cities.csv$: Walloon cities, fetched from \footnote{\url{https://nl.wikipedia.org/wiki/Lijst\_van\_gemeenten\_in\_het\_Waals\_Gewest}}.
        \item $submunicipalities.csv$: Belgian sub-municipalities, fetched from \footnote{\url{https://nl.wikipedia.org/wiki/Lijst\_van\_gemeenten\_in\_het\_Vlaams\_Gewest}}.
        \end{itemize}
    \item Documentation files
      	in directory \texttt{./target/installed/doc}
      	\begin{itemize}
        		\item Reference manual
        		\item User manual
        \end{itemize}
\end{compactitem}

@@

\begin{description}
    \item[\texttt{--config}] \ \\
        Specifies the run configuration parameters to be used for the simulation.
        If this is provided multiple times, the calibration is performed on all given simulations.
        It may be either \texttt{-c file=<file>} \texttt{or -c name=<name>}.
        The first option can be shortened to \texttt{-c <file>}, the second option accepts \texttt{TestsInfluenza}, \texttt{TestsMeasles} or \texttt{BenchMeasles} as  \texttt{<name}.
    \item[\texttt{--testcases}] \ \\
        Instead of providing the configuration files, you can also select multiple testcases to use for the simulation runs.
        The default is \texttt{influenza\_a, influenza\_b, influenza\_c, measles\_16} and \texttt{r0\_12}.
    \item[\texttt{--multiple}]\ \\
        The amount of simulations to run for each testcase. For each simulation, a different seed will be used.
    \item[\texttt{--single}]\ \\
        Run the simulations with the fixed seeds to determine the exact values.
    \item[\texttt{--output}]\ \\
        Write the results of the calibration to a file with given filename.
        This resulting file contains for each configuration and each step in the simulation the mean, standard deviation, exact value using the default seed and the values found with other seeds.
        These values depend on the selected options, specifically \texttt{--multiple} and \texttt{--single}.
    \item[\texttt{--write}]\ \\
        Write boxplots to files in the current directory. This creates an image for each config or testcase.
    \item[\texttt{--display}]\ \\
        Display the boxplots for the last step.
    \item[\texttt{--displayStep}]\ \\
        Display the boxplots for a specified step.
\end{description}
